%!TEX root = ../thesis.tex

%% ----------------------------------------------------------------------------
% BIWI SA/MA thesis template
%
% Created 09/29/2006 by Andreas Ess
% Extended 13/02/2009 by Jan Lesniak - jlesniak@vision.ee.ethz.ch
%% ----------------------------------------------------------------------------


\chapter{Introduction}
\label{cha:introduction}

Main goal: \textbf{weakly semi-supervised} instance object video segmentation.

% Give an introduction to the topic you have worked on:

% \begin{itemize}
%  \item \textit{What is the rationale for your work?} Give a sufficient description of the problem, e.g. with a general description of the problem setting, narrowing down to the particular problem you have been working on in your thesis. Allow the reader to understand the problem setting.
%  \item \textit{What is the scope of your work?} Given the above background, state briefly the focus of the work, what and how you did.
%  \item \textit{How is your thesis organized?} It helps the reader to pick the interesting points by providing a small text or graph which outlines the organization of the thesis. The structure given in this document shows how the general structuring shall look like. However, you may fuse chapters or change their names according to the requirements of your thesis.
% \end{itemize}


% \section{Focus of this Work}

% Which is the problem
The problem that this thesis have been trying to solve has been the segmentation of instances on images and videos.

% Who I tackled the problem
The solution proposed at the beggining consisted on focusing on video, try to track key points from instances.
The results weren't good, and that's why the we tried to tackle the problem using pixel embeddings.
With the pixel embeddings the instance segmentation on images was tackled.


% Aditional contributions I have made during my thesis
In adition to the research, I have contributed in side projects and research related with segmentation.
To help my research, and the others in the Segmentation Group at CVL, I developed a web interface which allowes to annotate and visualize results.
Also I have contributed on preparing the a new track on the segmentation field which consists on interactive segmentation. In relation with this, I helped collecting data with the annotation tool, and also develop a framework to evaluate interactive segmentation using human and automatic generated scribbles.




Structure:

Possible: One point to instance object segmentation on videos.

Talk about point tracking, and show results (Hourglass and ResNet heatmaps tracking).
Instance segmentation using metric learning a nd segment through similarity with keypoint.

1. State of the art

Point tracking with Hourglass to pose estimation

Instance object segmentation using metric learning


2. Method presented

Talk about the DeepLab ResNet architecture

Talked about the architecture to track the points

Talke about metric learning.

3. Experiments and Results

Talk about the datasets: PASCAL and DAVIS

Results on tracking points.

Results on Instance Segmentation with metric learning on Pascal

Show visual results on instance enbedding. Plot PCA for images and show that is possible to separate the instances.

Results on instance segmentation in DAVIS taking a GT keypoint (maximum performance on J gerater than OSVOS and nearly equal to ONAVOS).

Segmenting from keypoint on first frame gives 0.44

Traking the keypoint on first frame and segment from tracked keypoints gives almost the same result.

Point tracking should be improved.

4. Conclusion and Future Work

Very few methods for point tracking (mostly for object tracking). Tracking embeddings seems to not be a good solution, neither using resnet and finetune on a single instance (The method would require a high computational cost)

Use some method that capture more contest from the point sorrounding.

Embedding learning looks promising.



Then give results
% \section{Thesis Organization}
