%!TEX root = ../thesis.tex

\chapter{State of the Art}
\label{cha:stateofart}

% Describe the other's work in the field, with the following purposes in mind:

% \begin{itemize}
%  \item \textit{Is the overview concise?} Give an overview of the most relevant work to the needed extent. Make sure the reader can understand your work without referring to other literature.
%  \item \textit{Does the compilation of work help to define the ``niche'' you are working in?} Another purpose of this section is to lay the groundwork for showing that you did significant work. The selection and presentation of the related work should enable you to name the implications, differences and similarities sufficiently in the ``discussion'' section.
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this chapter, we summarize the most relevant work on instance object segmentation. 
First, we focus on tracking implementations and later we talk about state of the art methods for object instance segmentation and some implementations applied to video.

\section{Tracking}

Tracking implementations are mainly focus on object tracking. This conists on taking the bounding box sorrounding and object and make bounding box predictions throught the video that contains the object to track.

One state of the art implementation is called MDNet~\cite{nam2016learning}.
This implementation was the winner of the VOT Challenge~\cite{VOT_TPAMI} in 2016.


Unfortunetly there are not implementations that focus on keypoints tracking which is the idea behind this thesis.


For the purpose of tracking two related state of the art works which one is a NN object tracker:

MDNET~\cite{nam2016learning}.

% And the other one is state of the art for pose estimation:

% Stacked Hourglass Networks for Human Pose Estimation~\cite{newell2016stacked}


\section{Instance Segmentation}

Mask RCNN~\cite{he2017mask}: Use proposal and comes from work in object detection. Obtain state of the art results. But complex network with multiple proposal candidates.

Proposal Free network~\cite{liang2015proposal}.

OSVOS~\cite{caelles2017one} and ONAVOS make instance segmentation on video.

Deep metric learning for instance object segmentation~\cite{fathi2017semantic}.
